### 2022-02-01 documentos/intro.tex
etc
notas intro y mas etc

\section{Introduction} % {{{
Several PRA articles go straight into matter. I guess we will write what we have to write

@@

Nathanson, Ruskai~\cite{nathanson2007pauli} based on MUBs... Based on mutually unbiased measurements~\cite{Siudzinska2020}
Generalization of \textit{completely decoherence Pauli channels}, such as completely dephasing,
\begin{equation}
\rho \mapsto \rho_{00}\projj{0}+\rho_{11}\projj{1},
\end{equation}
and \textit{completely depolarizing},
\begin{equation}
\rho \mapsto \frac{\one}{2} \tr \rho,
\end{equation}
These channels correspond in collapsing the Bloch sphere into a line and a point, respectively. [...] Other families of channels inspired in leaving 
% }}}

>>>>

\section{Introduction} % {{{
\ddnote{Generalization of the notion that squeezing the Bloch sphere into a disk is not a channel. Quantum channels have a astonishing number of parameters as the dimension grows, so studies like ours is important to understand less parametric families of quantum channels. }
Several PRA articles go straight into matter. I guess we will write what we have to write

@@

\ddnote{Yo agregare un parrafo delineando la literatura alrededor de Ruskai}
Nathanson, Ruskai~\cite{nathanson2007pauli} based on MUBs... Based on mutually unbiased measurements~\cite{Siudzinska2020}
Generalization of \textit{completely decoherence Pauli channels}, such as completely dephasing,
\begin{equation}
\rho \mapsto \rho_{00}\projj{0}+\rho_{11}\projj{1},
\end{equation}
and \textit{completely depolarizing},
\begin{equation}
\rho \mapsto \frac{\one}{2} \tr \rho,
\end{equation}
These channels correspond in collapsing the Bloch sphere into a line and a point, respectively. [...] Other families of channels inspired in leaving 
% }}}

### 2022-02-01 documentos/proofdiagonalization.tex
ALL SORTS OF THINGS
Saint Pipeline, please give me the green light
notas intro y mas etc

reserve the Greek ones for quaternary ones \afnote{(and
reserve Greek letters for quaternary ones)}. 

@@

and its inverse relation,

@@

(-1)^{l  k+j m }\right) 

@@

@@

\afnote{Creo que es mejor dejar el tau dentro del parentesis para dejar implícito que está sumando también.}

@@

The eigenvalues read \

@@

\lambda_{jk}=\frac{1}{2}\sum_{l m } 
(-1)^{jl +k m }
\tau_{l m },

@@

For the sake of convenience in the demonstration of several useful properties
of the PCE channels, 
we shall reorder the eigenvalues, to write 
\begin{equation}
\lambda =  \frac12 \sa \tau
\end{equation}
with 
\begin{equation}
\sa=\left(
\begin{array}{cccc}
1 &1 &1   &1   \\
 1 & 1  & -1&-1   \\
1  & -1  & 1 & -1\\
1&-1&-1&1  
\label{a_appendix}
\end{array}
\right),
\end{equation}
instead of $H\otimes H$. This can be done due to the fact
that both matrices ($\sa$ and $H \otimes H$) are equivalent up to a permutation of rows. In other words
this operation corresponds to a relabeling in the eigenvalues $\lambda_{mn}$.
% }}}
\subsection{$N$ qubits} % {{{
To work out the $N$ qubit case, we again rely on binary indices. In this case, we replace 
$N$ dimensional vector $\valpha$ with a pair of $N$ dimensional vector binary
indices $\vec j$ and $\vec k$ so that 
each entry $\alpha_i$ of $\valpha$ is identified with the pair $j_i$ and $k_i$ as in the 
single qubit case of the previous subsection. Then, all the steps leading to 
\eref{eq:lambda:is:tau:appendix} can be redone, but with vector indices instead of binary scalars.

The tensor product of Pauli matrices, in vector form,  will be denoted by 
$\kket{\sigma_{\vec{k}\vec{l} }} = \kket{\sigma_{k_1l_1}}\otimes \cdots \otimes \kket{\sigma_{k_Nl_N}}$
and fulfill the orthogonality relation 
$\bbrakket{\sigma_{\vec{k}\vec{l} }}{\sigma_{\vec{k}'\vec{l}'}} = 
2^N \delta_{\vec{k}\vec{k}'}\delta_{\vec{l}\vec{l}'}$. 
% \begin{equation}
% \bbrakket{\sigma_{\vec{k}\vec{l} }}{\sigma_{\vec{k}'\vec{l}'}} = 2^N \delta_{\vec{k}\vec{k}'}\delta_{\vec{l}\vec{l}'}.
% \end{equation}
With this in mind, a $N$-qubit Pauli map can be written as 
% 
% 
% Analogously to the previous case, we can define an arbitrary Pauli map acting on $N$ qubits density matrices in terms of the tensor products of vectorized Pauli matrices
\begin{equation}
\hat{\mathcal{E}}_N = 
  \frac{1}{2^N}\sum_{\vec{l}\vec{m}} \tau_{\vec{l}\vec{m}} \ddyada{\sigma_{\vec{l}\vec{m} }}. 
\end{equation}
The generalization of \eref{CompToPau} and \eref{PauToComp} read \afnote{eq. $\to$ Eq.}
\begin{align}
\kket{\sigma_{\vec{\mu}\vec{\nu} }}  & = 
   \sum_{\vec{j}} (-1)^{\vec{j}\cdot\vec{\mu}} \kket{\vec{j},\vec{j}\oplus \vec{\nu}},\\
%
 \kket{\vec{l},\vec{l}\oplus \vec{n}} & = 
   \frac{1}{2^N}\sum_{\vec{m}} (-1)^{\vec{m}\cdot\vec{l}}\kket{\sigma_{\vec{m}\vec{n} }}.
\end{align}
\afnote{Cambiar los $\mu$ y $\nu$ por indices latinos.}

@@

Thus the eigenvalues of the Choi matrix $\mathcal{D}_N$ may be written as
\afnote{Creo que esta ultima linea se puede borrar.}

@@

\lambda_{\vec{j}\vec{n}}= \frac{1}{2^{N}}\sum_{\vec{l}\vec{m}} 
    (-1)^{\vec{j}\cdot\vec{l}+\vec{k}\cdot\vec{m}}

@@

\afnote{Aqui los vectores $l$ y $m$ en el exponente estan cambiados}

>>>>

reserve Greek letters for quaternary ones. 

@@

and its inverse relation \ddnote{falta definir que es el $\oplus$ en este contexto, y no solo eso, sino quienes son los vectores del lado derecho, \ie{} $\kket{k,l}$},

@@

(-1)^{j m + k l}

@@

\right) 

@@

@@

The eigenvalues read 

@@

\lambda_{jk}=\frac{1}{2}\sum_{l m } (-1)^{j m + k l} \tau_{l m },
% \lambda_{jk}=\frac{1}{2}\sum_{l m } (-1)^{jl +k m } \tau_{l m },

@@

For the sake of convenience in the demonstration of several useful properties
of the PCE channels, 
we shall reorder the eigenvalues, to write 
\begin{equation}
\lambda =  \frac12 \sa \tau
\end{equation}
with 
\begin{equation}
\sa=\left(
\begin{array}{cccc}
1 &1 &1   &1   \\
 1 & 1  & -1&-1   \\
1  & -1  & 1 & -1\\
1&-1&-1&1  
\label{a_appendix}
\end{array}
\right),
\end{equation}
instead of $H\otimes H$. This can be done due to the fact
that both matrices ($\sa$ and $H \otimes H$) are equivalent up to a permutation of rows. 
In other words this operation corresponds to a reordering of the eigenvalues.

% }}}
\subsection{$N$ qubits} % {{{
To work out the $N$ qubit case, we again rely on binary indices. In this case, we replace 
$N$ dimensional vector $\valpha$ with a pair of $N$ dimensional vector binary
indices $\vec j$ and $\vec k$ so that 
each entry $\alpha_i$ of $\valpha$ is identified with the pair $j_i$ and $k_i$ as in the 
single qubit case of the previous subsection. Then, all the steps leading to 
\eref{eq:lambda:is:tau:appendix} can be redone, but with vector indices instead of binary scalars.

The tensor product of Pauli matrices, in vector form,  will be denoted by 
$\kket{\sigma_{\vec{k}\vec{l} }} = \kket{\sigma_{k_1l_1}}\otimes \cdots \otimes \kket{\sigma_{k_Nl_N}}$
and fulfill the orthogonality relation 
$\bbrakket{\sigma_{\vec{k}\vec{l} }}{\sigma_{\vec{k}'\vec{l}'}} = 
2^N \delta_{\vec{k}\vec{k}'}\delta_{\vec{l}\vec{l}'}$. 
% \begin{equation}
% \bbrakket{\sigma_{\vec{k}\vec{l} }}{\sigma_{\vec{k}'\vec{l}'}} = 2^N \delta_{\vec{k}\vec{k}'}\delta_{\vec{l}\vec{l}'}.
% \end{equation}
With this in mind, a $N$-qubit Pauli map can be written as 
% 
% 
% Analogously to the previous case, we can define an arbitrary Pauli map acting on $N$ qubits density matrices in terms of the tensor products of vectorized Pauli matrices
\begin{equation}
\hat{\mathcal{E}}_N = 
  \frac{1}{2^N}\sum_{\vec{l}\vec{m}} \tau_{\vec{l}\vec{m}} \ddyada{\sigma_{\vec{l}\vec{m} }}. 
\end{equation}
The generalization of Eqs.~(\ref{CompToPau}) and (\ref{PauToComp}) read 
\begin{align}
\kket{\sigma_{\vec{k}\vec{l} }}  & = 
   \sum_{\vec{j}} (-1)^{\vec{j}\cdot\vec{k}} \kket{\vec{j},\vec{j}\oplus \vec{l}},\\
%
 \kket{\vec{l},\vec{l}\oplus \vec{n}} & = 
   \frac{1}{2^N}\sum_{\vec{m}} (-1)^{\vec{m}\cdot\vec{l}}\kket{\sigma_{\vec{m}\vec{n} }}.
\end{align}
% \afnote{Cambiar los $\mu$ y $\nu$ por indices latinos.}

@@

% Thus the eigenvalues of the Choi matrix $\mathcal{D}_N$ may be written as
% \afnote{Creo que esta ultima linea se puede borrar.}

@@

\lambda_{\vec{j}\vec{k}}= \frac{1}{2^{N}}\sum_{\vec{l}\vec{m}} 
    (-1)^{\vec{j}\cdot\vec{m}+\vec{k}\cdot\vec{l}}

@@
